\chapter{Solving differential equations}

Before you start talking about solving a single partial differential equation (PDE) or PDE system, as well as about neural networks, you need to clearly understand what methods exist to solve this problem, how they work, what strengths and weaknesses, what facts affect quality decision. After that, you also need to understand how regression models are constructed, evaluated, and explained. Thus, starting with the simplest linear regression model, results will be obtained that will allow us to construct good approximations based on Fourier or Chebyshev series from the available data or the available quality function. One of the most important results related to the approximation of functions is a model of artificial neural networks based on a sigmoid function. Tsybenko’s theorem guarantees the convergence of model parameters to the desired function with arbitrary accuracy, for example. When considering differential equations and solving them based on the method of artificial neural networks, questions regarding the construction, training and reduction of the number of parameters will be revealed.

\section{Regression and regularization introduction}
\input{chapters/chapter2/chapter2_regression_regularization}

\section{Regression as one of the types of expansion of function into functional series}
The linear regression model looks like expanding some unknown function in a series into predefined functions \eqref{eq:linear_expansion}. If we assume that $ \phi_i = cos $, then linear regression is transformed into an expansion of the function into a Fourier series, but without the mutual orthogonality of its terms. Instead of Fourier expansion, any functions, Chebyshev polynomials or Legendre polynomials can be used. In this section, we will discuss some expansions that are useful for further work.

\input{chapters/chapter2/chapter2_fourier}
\input{chapters/chapter2/chapter2_chebyshev}
\input{chapters/chapter2/chapter2_another}

\section{Differention equations}
\input{chapters/chapter2/chapter2_de_intro}
\input{chapters/chapter2/chapter2_de_solving}
\input{chapters/chapter2/chapter2_conclusions}